### 2017-09-08 paper/evaluation.tex

%% Table header macros
% $\Uparrow_\text{speed}$
\newcommand{\subcolA}{$\text{speedup}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\blankentry}{\entry{-}{-}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1 & #2}

\begin{table*}[t]
\centering
\small
\setlength{\tabcolsep}{2pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T$ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{1.85x}{0.23\%} & \entry{3.36x}{3.1\%}\\%

Facebook Linkbench   & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{1.54x}{0\%} & \entry{1.59x}{0\%}\\%

GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{0.80x}{1.70\%} & \entry{0.80x}{1.70\%}\\%

Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{1.38x}{0\%} & \entry{1.57x}{0\%}\\ 
Jcabi Github                  & \entry{2.6m}{634} & \entry{2.10x}{0\%} & \entry{17.70x}{0\%} & \entry{28.80x}{0\%} & \entry{2.00x}{0\%} & \entry{2.89x}{0\%} \\%
JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{2.77x}{0\%} & \entry{9.00x}{0\%}\\%
MapDB  & \entry{8.2m}{5,324}  & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{1.71x}{0.98\%} & \entry{3.42x}{0.98\%}\\%
Moquette                      & \entry{3.7m}{169} & \entry{4.62x}{65.64\%} & \entry{3.36x}{32.92\%} & \entry{12.33x}{77.78\%} & \entry{2.47x}{22.53\%} & \entry{9.25x}{69.44\%} \\
RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\
Stripe Java                   & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{2.69x}{0\%} & \entry{8.60x}{11.63\%}\\%

\midrule

\textbf{Average}   & \entry{30.3m}{2,897.6} & \entry{2.40x}{7.59\%} & \entry{4.10x}{4.51\%} & \entry{9.45x}{10.32\%} & \entry{1.86x}{2.54\%} & \entry{4.19x}{8.68\%} \\%

%%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%
%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%

%% OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%% Jankotek MapDB               &  \entry{9.9m}{5218} & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{1.5x}{0\%} & \entry{1.7x}{0\%}\\%
%% Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%% Apache Giraph (\CodeIn{core})&  \entry{7.2m}{236}  & \entry{2.1x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}   & \entry{1.0x}{0\%} & \entry{1.0x}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
%% Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%% Stripe Java                  &  \entry{4.2m}{302}  & \entry{4.2x}{5.2\%}  & \entry{3.5x}{5.7\%}       & \entry{4.2x}{6.3\%} & \entry{1.0x}{0.3\%} & \entry{4.2x}{5.7\%}\\%
%% AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%

%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

\bottomrule%
\end{tabular}
\caption{Speedup versus Flakiness (\subcolB). Configuration
  \emph{\Seq{}} denotes the comparison baseline, which runs tests
  sequentially.  Columns $T$ and $N$ indicate time and number of
  tests, respectively.  Other columns show speedup and percentage of
  failing tests in different configurations, compared to
  \emph{\Seq{}}.}
\label{tab:rq6-table}
\end{table*}

>>>>

\input{flakiness-speedup-table}
